Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-13 doc/PRF2022/PRF_main.tex
updates

\begin{figure}
  \begin{center}
  \includegraphics[height=0.2\textheight]{multilamellar_shear_Energy}
    \includegraphics[height=0.2\textheight]{multilamellar_shear_MSD}\\
          \includegraphics[height=0.2\textheight]{multilamellar_shear_LocPar}
  \end{center}
      \caption{A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$. We compute the energy and the mean square displacement $MSD(t) = \frac{1}{N_b^2}\sum_{i=1}^{N_b} ||D(t)-D(0) ||_2$ where the matrix $D$ is the pairwise distance matrix at time $t$.    }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[height=0.2\textheight]{multilamellar_TG_Energy}
    \includegraphics[height=0.2\textheight]{multilamellar_TG_MSD}\\
    \includegraphics[height=0.2\textheight]{multilamellar_TG_LocPar}
  \end{center}
    \caption{A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[height=0.2\textheight]{checker_board_shear_Energy}
    \includegraphics[height=0.2\textheight]{checker_board_shear_MSD}\\
  \includegraphics[height=0.2\textheight]{checker_board_shear_LocPar}
  \end{center}
\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_2 = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[height=0.2\textheight]{checker_board_TG_Energy}
    \includegraphics[height=0.2\textheight]{checker_board_TG_MSD}\\
      \includegraphics[height=0.2\textheight]{checker_board_TG_LocPar}
  \end{center}
\caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
\end{figure}

>>>>

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
  \end{center}
      \caption{A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$. We compute the energy and the mean square displacement $MSD(t) = \frac{1}{N_b^2}\sum_{i=1}^{N_b} ||D(t)-D(0) ||_2$ where the matrix $D$ is the pairwise distance matrix at time $t$.    }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
  \end{center}
    \caption{A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
  \end{center}
\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
  \end{center}
\caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
  \end{center}
\caption{A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.1\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}
  \end{center}
\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1,0.2\}$. }
\end{figure}
